Boosted Regression Trees for Predictive Auto-Tuning

### 2011-12-14 paper/draft1.tex
m

% DDC: XXX are these figures still in?
Figure~\ref{fig:speedup} also shows that random hill-climbing is at least
competitive and often better than the hand-chosen grid approach
of~\citet{pinto+cox:2011gcg}.  Figure~\ref{fig:hcX} shows how the number of hill-climbing iterations
affects the quality of the auto-tuned model.
The quicker HC25 approach is clearly inferior but the quality of the 75 iteration search (HC75) is statistically similar to the shorter HC50, suggesting that XXX.
Still, HC75 is not always better than the grid, so evidently neither search algorithm is perfect.

The previous figures establish that auto-tuning on a problem-by-problem basis
can achieve good performance improvements over a high-quality reference
baseline, but they do not show how long it takes to find these implementations.
A search of 75 iterations took an average of about 120 seconds XXX on a fast
computer, because it requires compiling 75 CUDA kernels, and evaluating up to
750 filterbank correlations to get reliable timing information for each
candidate implementation.

\begin{figure}
\centering
\includegraphics[scale=.42]{fig_ntrain_munctional0_580.pdf} % on vader
\caption{The effect of the invalid configuration score ($a$) and training set
size on simulated auto-tuning.
All candidates timed during the grid and
hill-climbing search procedures were used as training points, so the training
set sizes ranged from an average of 1500 (10 problem configurations) to 30
thousand (200 problem configurations).
Training on 10 or 25 configurations was useful (higher mean than the reference),
but not as useful as training on 50 or more configurations.
The results on the GTX 295 suggest that
moderate values of $a$ between $0.25$ and $0.75$ might be
best, but $a$ had no significant effect on the GTX 480.
}
\label{fig:fig_ntrain}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=.42]{fig_ntrain_munctional0_580.pdf} % on vader
\caption{The effect of the invalid configuration score ($\zeta$) and training set
size on simulated auto-tuning.
All candidates timed during the grid and
hill-climbing search procedures were used as training examples, so the training
set sizes ranged from an average of 1480 (10 problem configurations) to 29 600
(200 problem configurations).
Training from the largest training sets took approximately 30 seconds
Models trained on as few as 25 configurations outperformed the reference.
Models trained
but not as useful as training on 50 or more configurations.
Moderate values of $\zeta$ between $\log(0.25)$ and $\log(0.75)$ are best.
}
\label{fig:fig_ntrain}
\end{figure}

### 2011-12-14 paper/scratch.tex
m

>>>>

% DDC: XXX are these figures still in?
Figure~\ref{fig:speedup} also shows that random hill-climbing is at least
competitive and often better than the hand-chosen grid approach
of~\citet{pinto+cox:2011gcg}.  Figure~\ref{fig:hcX} shows how the number of hill-climbing iterations
affects the quality of the auto-tuned model.
The quicker HC25 approach is clearly inferior but the quality of the 75 iteration search (HC75) is statistically similar to the shorter HC50, suggesting that XXX.
Still, HC75 is not always better than the grid, so evidently neither search algorithm is perfect.

The previous figures establish that auto-tuning on a problem-by-problem basis
can achieve good performance improvements over a high-quality reference
baseline, but they do not show how long it takes to find these implementations.
A search of 75 iterations took an average of about 120 seconds XXX on a fast
computer, because it requires compiling 75 CUDA kernels, and evaluating up to
750 filterbank correlations to get reliable timing information for each
candidate implementation.
